CTest Integration of Sikuli Automated GUI Testing

### 2011-06-17 Documentation/Article.tex
limitations

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Evan Schwab, Lydie Souhait, Nicolas Rannou, Kishore Mosaliganti\\
Arnaud Gelas, Sean Megason}
\authoraddress{Harvard Medical School, Megason lab}

@@

\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.99\textwidth]{Images/SimpleSikuliExample.png}
 % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280 1024
 \caption{Simple Sikuli Script Example in Sikuli-IDE}
 \label{fig:SimpleExample}
\end{figure}

@@

@@

\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.99\textwidth]{Images/Gofigure2GUI.png}
 % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280 1024
 \caption{GoFigure2 GUI Interface}
 \label{fig:GoFigure2GUI}
\end{figure}

\begin{figure}[htp]
 \centering
 \includegraphics[width=0.99\textwidth]{Images/Gofigure2Example.png}
 % Gofigure2Example.png: 667x826 pixel, 72dpi, 23.53x29.14 cm, bb=0 0 667 826
 \caption{Sikuli Script for Gofigure2 GUI Testing}
 \label{fig:Gofigure2Example}
\end{figure}

@@

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Evan Schwab, Arnaud Gelas, Lydie Souhait, Nicolas Rannou,\\
Kishore Mosaliganti, Sean Megason}
\authoraddress{Megason Lab, Department of Systems Biology, Harvard Medical
School}

@@

\begin{figure}[tbp]
 \centering
 \includegraphics[width=0.99\textwidth]{Images/SimpleSikuliExample.png}
 % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280 1024
 \caption{Simple Sikuli Script Example in Sikuli-IDE}
 \label{fig:SimpleExample}
\end{figure}

@@

\begin{figure}[tbp]
 \centering
 \includegraphics[width=0.99\textwidth]{Images/Gofigure2GUI.png}
 % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280
 \caption{GoFigure2 GUI Interface}
 \label{fig:GoFigure2GUI}
\end{figure}

@@

\begin{figure}[tbp]
 \centering
 \includegraphics[width=0.99\textwidth]{Images/Gofigure2Example.png}
 % Gofigure2Example.png: 667x826 pixel, 72dpi, 23.53x29.14 cm, bb=0 0 667 826
 \caption{Sikuli Script for Gofigure2 GUI Testing}
 \label{fig:Gofigure2Example}
\end{figure}

@@

% ------------------------------------------------------------------------
\section{Current Limitation}

\subsection{Text Recognition}

\subsection{Off-screen Rendering}

\subsection{Variation of style between machines}
Different OS, different look => failures
Even on the same OS, GUI can look different = > failures

\subsection{CDash}
